---
title: "Congressional Election Survey Analysis"
output: html_document
date: '2022-11-17'
---

Import and clean up the data
```{r setup}
library(tidyverse)
library(knitr)
knitr::opts_chunk$set(echo = TRUE,
                      fig.asp = 0.618)
library(haven)
CCES14_AGT_OUTPUT_Feb2015_unmatched <- as_tibble(
  read_sav("./Data/CCES14_AGT_OUTPUT_Feb2015_unmatched.sav")
  )

unmatched_2014 <- CCES14_AGT_OUTPUT_Feb2015_unmatched %>% 
  filter(!is.na(AGT_Marijuana_Prime),
         !is.na(marijuana_treat),
         is.na(AGT301)) %>% 
  select(AGT_Weed, V101, AGT301, marijuana_treat, AGT_Marijuana_Prime, pid7, pid3, AGT_weedrand, educ) %>% 
  mutate(Elite_Cue = case_when(
    marijuana_treat == 1 ~ "Dem Negative",
    marijuana_treat == 2 ~ "Rep Negative",
    marijuana_treat == 3 ~ "Dem Positive", 
    marijuana_treat == 4 ~ "Rep Positive",
    marijuana_treat == 5 ~ "Control" 
  ),
  Party_Detail = as.factor(case_when(
    pid7 == 1 ~ "Strong Democrat",
    pid7 == 2 ~ "Not Strong Democrat",
    pid7 == 3 ~ "Lean Democrat",
    pid7 == 4 ~ "Independent",
    pid7 == 5 ~ "Lean Republican",
    pid7 == 6 ~ "Not Strong Republican",
    pid7 == 7 ~ "Strong Republican",
    pid7 == 8 ~ "Not Sure",
    pid7 == 98 ~ "Skipped",
    pid7 == 99 ~ "Not Asked"
  )),
  Party = as.factor(case_when(
    pid3 == 1 | pid7 == 3 & pid3 == 3 ~ "Democrat",
    pid3 == 2 | pid7 == 5 & pid3 == 3 ~ "Republican",
    pid3 == 3 & pid7 == 4 ~ "Independent",
    pid3 == 4 ~ "Other",
    pid3 == 5 ~ "Not Sure",
    pid3 == 8 ~ "Skipped",
    pid3 == 9 ~ "Not Asked"
  )),
  Ideological_Cue = as.factor(case_when(
    AGT_weedrand == 1 ~ "Society",
    AGT_weedrand == 2 ~ "Paternalistic",
    AGT_weedrand == 3 ~ "Control",
    AGT_weedrand == 8 ~ "Skipped",
    AGT_weedrand == 9 ~ "Not Asked"
  )),
  Education = as.factor(case_when(
     educ == 1 | educ == 2 | educ == 3 | educ == 4 ~"Less than BA",
     educ == 5 | educ == 6 ~ "BA or Higher"
  )))

```

Get sample sizes
```{r}
#n's

unmatched_2014 %>% 
  filter(Ideological_Cue == "Society",
         Party == "Democrat") %>% 
  nrow()

unmatched_2014 %>% 
  filter(Ideological_Cue == "Society",
         Party == "Republican") %>% 
  nrow()

```

Use renv to ensure reproducability
```{r eval = F}
# library(renv)
# renv::init()
```

find average support for marijuana legalization and create some confidence intervals
```{r}
#means
a = 0.05 # signifigance level

# mean by party
mean_party <- unmatched_2014 %>% 
  group_by(Party) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se) %>% 
  filter(Party == "Democrat" | Party == "Republican")
### a t-test of diff in means of weed approval by party, consistent with modern literature that there is a difference among party ID
filtered <- unmatched_2014 %>% 
  filter(Party == "Democrat" | Party == "Republican",
         !is.na(AGT_Weed))
reps <- filtered %>% 
  filter(Party == "Republican")
reps_weed <- reps$AGT_Weed
dems <- filtered %>% 
  filter(Party == "Democrat")
dems_weed <- dems$AGT_Weed
t.test(dems_weed, reps_weed)

## calculate the average support for legalization by party and ideological cue and construct confidence interval
means_ideology <- unmatched_2014 %>% 
  group_by(Party, Ideological_Cue) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)

## calculate the average support for legalization by education and ideological cue and construct confidence interval
ed_means_ideology <- unmatched_2014 %>% 
  group_by(Ideological_Cue, Education) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)

ed_party_ideology <- unmatched_2014 %>% 
  group_by(Ideological_Cue, Education, Party) %>% 
   summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)

## calculate average support for legalization by party and elite cue
means_elite <- unmatched_2014 %>% 
  group_by(Party, Elite_Cue) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)

## calculate average support for legalization by education and elite cue 
ed_means_elite <- unmatched_2014 %>% 
  group_by(Elite_Cue, Education) %>% 
   summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)

## avg support for legalization by education party and elite cue
ed_party_elite <- unmatched_2014 %>% 
  group_by(Elite_Cue, Education, Party) %>% 
   summarise(Avg = mean(AGT_Weed, na.rm = T),
            n = n(),
            sd = sd(AGT_Weed, na.rm = T),
            se = sd / sqrt(n),
            lower = Avg - qnorm(1 - a / 2)*se,
            upper = Avg + qnorm(1 - a / 2)*se)
#detailed party stuff; kind of useless
means_ideology_detail <- unmatched_2014 %>% 
  group_by(Party_Detail, Ideological_Cue) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T))

means_elite_detail <- unmatched_2014 %>% 
  group_by(Party_Detail, Elite_Cue) %>% 
  summarise(Avg = mean(AGT_Weed, na.rm = T))
```


Create a plot displaying average support for marijuana legalization by partisan cue political ideology. This plot suggests Democrats and Republicans differ on levels of support for marijuana legalization, but that their levels of support are largely unaffected by partisan cues, whether they be in-party or out-party cues 
```{r}
#plots
# elite cues
eliteplot <- means_elite %>% 
  filter(Party == "Democrat" | Party == "Republican" | Party == "Independent") %>% 
  mutate(Avg_for_label = round(Avg,2)) %>% 
  ggplot(aes(Elite_Cue,Avg))+
  geom_errorbar(aes(ymin = lower, ymax = upper))+
  geom_point(size = 12, shape=21, fill="White", color = "White")+
  theme_minimal()+
  facet_wrap(vars(Party))+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))+
  geom_text(aes(label=Avg_for_label))+
  labs(title = "Elite Cue",
       y = "",
       x = "")

eliteplot
```

Display plot for average support for marijuana legalization by ideological cue and party. This suggests that like the above plot, Republicans and Democrats are largely unswayed by ideological cues when it comes to support for marijuana legalization. 
```{r}
ideoplot <- means_ideology %>% 
  filter(Party == "Democrat" | Party == "Republican" | Party == "Independent") %>% 
  mutate(Avg_for_label = round(Avg,2)) %>% 
  ggplot(aes(Ideological_Cue,Avg))+
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.5)+
  geom_point(size = 12, shape = 21, fill = "White", color = "White")+
  theme_minimal()+
  facet_wrap(vars(Party))+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"))+
  geom_text(aes(label=Avg_for_label))+
  labs(title = "Ideological Prime - 2014",
       y = "",
       x = "")
ideoplot
```